\documentclass{resume}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Abhilash M A}
% ------ Address --------------------------------------------------------

\address{Technical Manager\\
  CYBOSOL (Nuevalgo Solutions Pvt Ltd)\\
  Technopark Phase III, Trivandrum\\
  Kerala, India\\
  {\em Ph:} (+91)-85-8901-5153}{
  {\em email:} \mbox{\small\tt abhidsm@gmail.com}\\
  {\em web:} \mbox{\small\tt abhidsm.com}\\
  {\em github:} \mbox{\small\tt github.com/abhidsm}\\
  {\em linkedin:} \mbox{\small\tt linkedin.com/in/abhidsm}\\
  {\em blog:} \mbox{\small\tt abhionrails.com}}

\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
  \citem{B-Tech in Computer Science \& Engineering (70\%)} \hfill \textbf{2005 -- 2008}
  \citemnobullet University of Calicut, Jyothi Engineering College, Kerala.
  \citem{Diploma, Computer Engineering (72.71\%)} \hfill \textbf{2002 -- 2005}
  \citemnobullet IPT \& GPTC Shoranur, Kerala.
  \citem{VHSE in Computer Science (73.71\%)} \hfill \textbf{2000 -- 2002}
  \citemnobullet GVHSS Shoranur, Kerala.
\end{category}

% --------- Research ----------------------------------------------------

\begin{category}{Research interests}
  \citemnobullet NoSQL databases, XMPP Server, iOS \& Android application development,
  Test Driven Development, development of Ruby Gems, Design Patterns, Clean Code.
\end{category}

\begin{category}{Technical Skills}
  \citembullet {\it Operating Systems}: GNU/Linux, Mac OSX, Microsoft Windows.
  \citembullet {\it Programming Languages}: Ruby, JavaScript, HTML5, CSS3,
  Objective C, Java, C\# .NET.
  \citembullet {\it Frameworks}: Ruby on Rails, ASP.NET, jQuery, RSpec, Jasmine.
  \citembullet {\it Databases}: MySQL, MongoDB, Redis.
  \citembullet {\it Tools}: Backbone.js, Sinon.js, jsTestDriver,
  Jenkins, Capistrano.
  \citembullet {\it Version Control}: Git.
  \citembullet {\it Cloud Platforms}: Google App Engine, Amazon EC2,
  Amazon S3, Openstack.
  \citembullet {\it Specialities}: Ruby, Rails, NoSQL databases, Web services, Automation \& deployment, 
  Android, iOS and Web application development, Test Driven
  Development, experienced in Agile software development
  methodologies, polyglot programmer, full stack developer.
\end{category}

% -------- Work experience --------------------------------------------

\begin{category}{Work \\experience}
  \citem{CYBOSOL (Nuevalgo Solutions), Technopark Phase III - Trivandrum}
  \citemnobullet \textbf{Technical Manager} \hfill \textbf{November 2014 -- present}
  \citemnobullet CYBOSOL (Nuevalgo Solutions) provides turnkey and custom solutions on desktop, web, mobile and cloud-based environments.
  \begin{itemize}
  \item \textbf{Messenger App} {\em Mar 2015 - present}: A chat
    application with features like register with phone number, sync
    phone contacts, chat with image, audio, video, location, contacts,
    Group chat, etc. The application is implemented using {\em Ruby on
      Rails, ejabberd xmpp server, ActiveAdmin, MySQL, iOS,
      Android}. \textbf{Role}: {\em Technical Manager}. 
  \item \textbf{Mobile Banking App} {\em Nov 2014 - present}: A mobile
    banking app for merchants and consumers. Merchant mobile app uses
    a swipe device to get the credit card details. The application has
    the features like balance enquiry, bill payment, card transfer,
    mini statement etc. The application uses SSL connection and PIN
    encryption to secure the transactions. Implemented using {\em Ruby
      on Rails, MySQL, MongoDB, iOS, Android}. \textbf{Role}: {\em
      Technical Manager}.\\\\\\ 
  \end{itemize}
  \citem{Nuevalgo Solutions, Infopark Thrissur}
  \citemnobullet \textbf{Product Lead} \hfill \textbf{August 2013 -- November 2014}
  \citemnobullet Nuevalgo is a product and services based company who delivers custom software for desktop, web, mobile and cloud-based environments.
  \begin{itemize}
  \item \textbf{GroupBuy} {\em Aug 2013 - present}: A social
    e-commerce application where customers can search, request or buy
    products. Login and share with Social networks. Purchase products
    using debit/credit cards and paypal. Also merchants can use this
    app to sell their products. Implemented using {\em Ruby on Rails,
      ActiveaAdmin, Backbone.js, MySQL, MongoDB, iOS, Android}. \textbf{Role}: {\em Product lead}. 
  \item \textbf{Project Tracker} {\em Oct 2013 - present}: Initially
    started as an Internal time tracking application which has grown
    in to a product that helps other    organizations to track their
    projects. Mainly Projects, Tasks and Activities. It also includes
    Bug tracking and Opportunity/Lead tracking. This is a SaaS app
    which uses {\em Ruby on Rails, MySQL, Active Admin, Android, iOS}. \textbf{Role}: {\em Product lead}. 
  \item \textbf{Ebook Application} {\em May 2014 - Oct 2015}: Ebook is
    a web/mobile app where the main functionality is Ebook
    reader. There are more features like Bookmark, Notes, Highlight,
    Voice Read, Translate, Favorites, Share with Social networks,
    Social network login, multi language support, file converter (PDF,
    DOC to Epub) etc. Implemented using {\em Ruby on Rails, MySQL,
      Calibre, Open Office, Apache Solr, iOS, Android,
      Angular.js}. \textbf{Role}: {\em Product lead}. 
  \end{itemize}
  \citem{Multunus Software Private Limited, Bangalore}
  \citemnobullet \textbf{Product Developer} \hfill \textbf{May 2010 -- July 2013}
  \citemnobullet Multunus is a custom software development boutique
  which builds Web and Mobile applications that are inherently
  complex and risky.\\Multunus practices Extreme Programming and Continuous
  Delivery to rapidly ship quality software. Ruby on Rails, HTML5, Android and iOS are the technologies of choice.
  \begin{itemize}
  \item \textbf{TIMS} {\em Apr 2013 - Jun 2013}: This is a data centric web application which uses {\em Ruby on Rails, Backbone.js, MySQL, MongoDB and Redis}. \textbf{Role}: {\em Team lead}. 
  \item \textbf{GoCapital.Asia} {\em Nov 2012 - Mar 2013}: GoCapital.Asia is a
    platform to connect startups with investors and talent i.e. to
    help them raise capital and recruit the right team. This is a web
    applications developed using {\em Ruby on Rails and MySQL}. \textbf{Role}:
    {\em Team lead}.
  \item POC mobile applications using {\em Android, iOS, and PhoneGap}.
  \item \textbf{Nimit} {\em Feb 2012 - Jul 2012}: Nimit is sophisticated
    product for personalized education with lots of features. The
    scope of the product is very wide but providing better education
    to Students is one of the goals. Worked on front end for
    developing single page application with {\em Backbone.js, jQuery,
      HTML5, CSS3, Jasmine, JS TestDriver, Sinon.js}. \textbf{Role}: {\em Team Lead}.
  \item \textbf{ElixirHealth} {\em Feb 2011 - Jun 2011}: A social networking web app for the HealthCare
    domain, which connects people to the health professionals. {\em
      Ruby on rails, Refinery CMS, Solr, Sunspot, JS Testdriver,
      RSpec2}. \textbf{Role}: {\em Developer}.
  \item \textbf{Publink} {\em Jul 2010 - Jan 2011}: Developed location aware service that enables Public Radio
    stations connect Local Businesses with the Local community. {\em Ruby on Rails, Geokit, Rspec}. \textbf{Role}: {\em Developer}.
  \item Developed Outlook plugin using {\em C\#.NET, VSTO}. \textbf{Role}: {\em Developer}.
  \end{itemize}
  \citem{AikoInfotech, Thrissur} 
  \citemnobullet \textbf{Software Programmer} \hfill \textbf{July 2008 -- April 2010}
  \citemnobullet Aiko Infotech is a software and networking solutions
  company. Main business areas include IT Consultancy, Software and Network
  Training, Software Solutions, Networking Solutions.
  \begin{itemize} 
  \item \textbf{IGPTest}: Graphical Application using {\em C\#.NET}. \textbf{Role}: {\em Programmer}.
  \item \textbf{MasNetway}: Web based Business application and Multi Level Marketing
    application using {\em ASP.NET, C\#.NET and MS SQL}. \textbf{Role}: {\em Programmer}.
  \item Standalone application for a Business System using {\em C\#.NET and MS SQL}.
  \end{itemize}
\end{category}

% -------- Awards & Honours ---------------------------------------

\begin{category}{Awards \&\\ Honours}
  \citem{``Best Performance Award''}, {\em
    CYBOSOL (Nuevalgo Solutions)}. \hfill \textbf{2014}
  \citem{``Star of Nuevalgo''}, {\em Nuevalgo Solutions}. \hfill \textbf{2013}
  \citem{``Star of the year''}, {\em Multunus Software Private Limited}. \hfill \textbf{2010}
  \citem{Attended ``Agile India''}, {\em Banglore}. \hfill \textbf{2013}
  \citem{Attended ``Ruby Conf India''}, {\em Banglore}. \hfill \textbf{2011}
  \citem{Attended ``Droid Con''}, {\em Banglore}. \hfill \textbf{2011}
\end{category}


% -------- Opensource -------------------------------------------

\begin{category}{Opensource}
  \citemnobullet List of major opensource contributions. Refer GitHub for source code.
  \citembullet \textbf{time\_diff}: Ruby Gem which calculates the difference between two times.
  \citembullet \textbf{OrphanRecords}: Ruby Gem which show/delete the orphan records in your Rails application
  \citembullet \textbf{who-is-next}: An android application which helps us to keep in touch with friends and relatives.
\end{category}

% -------- Reference --------------------------------------------

\begin{category}{Reference}
  \citemnobullet \\
  \begin{tabular}{ll}Shihabudheen P K&Aity A K\\
    CEO&Director\\
    Winwius Techno Solutions&Aiko Infotech\\
    Infopark, Kochi, Kerala&Thrissur, Kerala\\
    Email: \mbox{\small\tt shihabudheen.pk@gmail.com}&Email: \mbox{\small\tt mailofaity@gmail.com}\\
    Ph: (+91)-99-6142-9066&Ph: (+91)-99-6198-5477
  \end{tabular}
\end{category}
\end{document}
